---
title: "Data Science Capstone (Week 7) Slides"
author: "QW"
date: "2023-06-15"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown
Data Science Capstone (Week 7)
Shiny app to project the next word.

## Introduction
The goal of this exercise is to create a product to highlight the prediction algorithm that you have built and to provide an interface that can be accessed by others. For this project you must submit:

A Shiny app that takes as input a phrase (multiple words) in a text box input and outputs a prediction of the next word.


## Shiny App we developed to project the next word

```{r}
library(shiny)
library(stringr)
library(tm)
library(purrr)
library(ngram)

# Define UI for application that draws a histogram
fluidPage(

    # Application title
    titlePanel("Data Science Capstone Final Project at Week 7"),
    sidebarLayout(
        sidebarPanel(
            textInput("inputText", "This apps can predict the next word to your input",value = ""),
            br(), 
            submitButton("Predict"),
            hr(),
            helpText("Click on the Predict button above to predict the next word", 
                     hr(),
                     "The brief output from R.")
        ),
        mainPanel(
            strong("My input:"),
            strong(code(textOutput('inputsentence'))),
            br(),
            strong("The projected word:"),
            strong(code(textOutput('thenextword'))),
            hr(),
            h2("R output"),
            verbatimTextOutput("prediction")
        )
    )
)

```


## Shiny App we developed to project the next word
During the development of this prediction Shiny App (https://qiuqingw.shinyapps.io/finalshinyapp/), we firstly created three matrixs containing two-word, three-word and four-word patterns. And then we wrote a new function "projectnextword", which is used to predict the most frequent word after your input.
The related R-codes are listed here (https://github.com/qiuqingw/dscw7_shinyapp/blob/main/app.R).
Thank you for your time and review!
```{r}
```


